---
title: "Bridges Homework"
author: "Steven Xia"
date: "2/5/2021"
output: github_document
---

[**My Github Repository Here**](https://github.com/sxia35/BridgesHomework.git)

```{r include=FALSE}
library(tidyverse)
```

**After I went on the Federal Highway Administration's website, I downloaded Washington D.C.'s bridge data from 2019, and loaded the text file into a frame: *districtColumbia*.**

```{r}
districtColumbia <- read_csv("https://www.fhwa.dot.gov/bridge/nbi/2019/delimited/DC19.txt")
```

**Upon inspection, this data has over 100 columns, which is way too many. Thus I subsetted *districtColumbia* into a smaller tibble containing only variables that I want - such as bridge ID and FIPS codes.**

```{r}
districtColumbiaSmall <- select(districtColumbia, STRUCTURE_NUMBER_008, YEAR_BUILT_027, 
                                STATE_CODE_001, COUNTY_CODE_003, PLACE_CODE_004,
                                DECK_COND_058, SUPERSTRUCTURE_COND_059, SUBSTRUCTURE_COND_060,
                                CHANNEL_COND_061, CULVERT_COND_062, OPR_RATING_METH_063,
                                OPERATING_RATING_064, INV_RATING_METH_065, INVENTORY_RATING_066)
                                
head(districtColumbiaSmall)
```

**Below, I made a plot with the variables *Deck Condition* and *Year Built*.**

```{r}
ggplot(districtColumbiaSmall, aes(x = YEAR_BUILT_027, y = DECK_COND_058)) +
  geom_jitter(width = 0.25) + 
  labs(
    x = "Year Built",
    y = "Deck Condition",
    title = "Bridge Condition in Washington D.C.") 
```